Global study of well-being and internet adoption | Online analysis supplement

### 2021-11-18 03-analysis.Rmd
More post processing

```{r}
f2d <- fits_2c %>% 
  mutate(
    out = 
      map(
        fit, 
        ~as_draws_df(., variable = "^b_|^sd_|^cor_", regex = TRUE) %>% 
          summarise_draws(samples = length, default_convergence_measures())
        )
    ) %>% 
  select(-fit) %>% 
  unnest(out)
f2d %>%  
  kbl(
    caption = "HMC Diagnostics, Model 2c",
    digits = c(0,0,0,2,0,0)
  ) %>% 
  kable_paper(html_font = Font, full_width = FALSE) %>% 
  column_spec(
    4, 
    color = "white",
    background = spec_color(
      f2d$rhat, 
      direction = 1, 
      option = "C", 
      end = .7
    )
  ) %>% 
  scroll_box(height = "600px", width = "800px")
```

@@

```{r}
fits_2 <- reduce(
  list(
    fits_2b %>% rename(fit_2b = fit), 
    fits_2c %>% rename(fit_2c = fit)
  ), 
  left_join
) %>% 
  pivot_longer(fit_2b:fit_2c, names_to = "model", values_to = "fit")
fits_2 %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws_df(.x, variable = "^b_", regex = TRUE) %>% 
        summarise_draws(
          mean, quantile, rhat, 
          .args = list(probs = c(.025, .975))
        )
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(
    result = str_glue(
      "b = {mean} ({`2.5%`}, {`97.5%`}) [rhat = {round(rhat, 2)}]"
    )
  ) %>% 
  select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
  pivot_wider(names_from = model, values_from = result) %>% 
  kbl() %>% 
  kable_paper(html_font = Font)
```

@@

```{r}
fits_brm_internet_interactions %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
        summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95)))
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  # filter(str_detect(variable, "_i1_cw|b$")) %>% 
  kbl(digits = 3) %>% 
  kable_minimal(full_width = FALSE)
```

>>>>

```{r}
fits_2c <- tibble(
  cause = c("Anxiety", "Depression"),
  fit = list(read_rds("output/brm-2c-Anxiety.rds"), read_rds("output/brm-2c-Depression.rds"))
)
f2d <- fits_2c %>% 
  mutate(
    out = 
      map(
        fit, 
        ~as_draws_df(., variable = "^b_|^sd_", regex = TRUE) %>% 
          summarise_draws(samples = length, default_convergence_measures())
        )
    ) %>% 
  select(-fit) %>% 
  unnest(out)
f2d %>%  
  kbl(
    caption = "HMC Diagnostics, Model 2c",
    digits = c(0,0,0,2,0,0)
  ) %>% 
  kable_paper(html_font = Font, full_width = FALSE) %>% 
  column_spec(
    4, 
    color = "white",
    background = spec_color(
      f2d$rhat, 
      direction = 1, 
      option = "C", 
      end = .7
    )
  ) %>% 
  scroll_box(height = "600px", width = "800px")
```

@@

```{r}
fits_2c %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws_df(.x, variable = "^b_", regex = TRUE) %>% 
        summarise_draws(
          mean, quantile, rhat, 
          .args = list(probs = c(.025, .975))
        )
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(
    result = str_glue(
      "b = {mean} ({`2.5%`}, {`97.5%`})"
    )
  ) %>% 
  select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
  pivot_wider(names_from = cause, values_from = result) %>% 
  kbl() %>% 
  kable_paper(html_font = Font)
```

@@

```{r}
tmp <- fits_2c %>% 
  mutate(
    out = map(
      fit, 
      ~emtrends(.x, var = "i1_cw", by = c("sex", "age"))
    )
  ) %>% 
  select(-fit)
tmp %>% 
  mutate(out = map(out, ~as.data.frame(out))) %>% 
  unnest(out) %>% 
  select(cause, sex, age, i1_cw.trend, lower.HPD, upper.HPD) %>% 
  kbl(digits = 3) %>% 
  kable_minimal(full_width = FALSE)
```
